Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-11-20 analysis/paper/sim_survey_paper.Rmd
Finish drafting rejigged methods section

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
Sys.setenv("MAPBOX_TOKEN" = "pk.eyJ1IjoicGF1bHJlZ3VsYXIiLCJhIjoiY2pueGIxejMxMGM0MjNqbjR1aXdwYm92bSJ9.R-t1SCa0VHKf4N-PQmYI5Q")
# load("analysis/cod_sim_exports/2018-10-26_age_clust_test/test_output.RData")
source("analysis/paper/helper_functions.R")
```

@@

| `> n <- sim_abundance(`                                 |                                       *Simulate abundance* |                            |         

@@

| `> g <- make_grid(`                                     |                                              *Make a grid* |                            |

@@

| `> d <- sim_distribution(`                              |                                    *Simulate distribution* |                            |     
| `+   sim = n,`                                          |                Object produced by `sim_abundance` function |                            |     
| `+   grid = g,`                                         |                    Object produced by `make_grid` function |                            |

@@

| `> e <- expand_surveys(`                                |                       *Define a series of surveys to test* |                            |

@@

| `> s <- test_surveys(`                                  |                             *Simulate and analyze surveys* |                            |
| `+   sim = d,`                                          |             Object produced by `sim_distribution` function |                            |
| `+   surveys = e,`                                      |               Object produced by `expand_surveys` function |                            |

@@

As noted above, the amount of RAM a user's computer has may limit the utility of the `sim_survey` function for running thousands of simulations of the same survey. The `sim_survey_parallel` function was therefore constructed to facilitate the running of thousands of simulations without running into RAM limitations. This function is set-up to run multiple `sim_survey` calls in parallel using the doParallel package [@weston2015] and, as such, multiple loops can be run using the `n_loops` argument and within each loop multiple simulations can be run (controled using the `n_sims` argument). Total simulations will be the product of `n_loops` and `n_sims` arguments. If more than one core (`cores`) is specified, then the simulations will be run in parallel to speed up the process. Low numbers of `n_sims` and high numbers of `n_loops` will be easier on RAM, but may be slower. The optimum ratio of `n_sims` to `n_loops` will depend on the amount of RAM and number of cores the user's computer has. In any case, this function simplifies the process of running thousands of simulations of the same survey and the simulated data can then be supplied to survey-based or model-based analyses that require simulation testing.

@@

## Testing protocol

...

@@

Like any model, this simulation is a simplification of a much more complex reality. For instance, the population is assumed to aggregate by age-class and be uniformly distributed within a cell when, in the real-world, they may aggregate by length and form finer-scale clusters. The survey is also an instantaneous snapshot of the population, meaning that the population is assumed to be in the same location from the beginning to the end of the survey. Also, fish are aged at random within length bins and ages are estimated without error. Finally, area trawled is assumed to be perfectly standard. This is a short, non-inclusive, list of additional variability that likely occurs in the real-world but was not implemented here for simplicity.

@@

```{r icc, cache = TRUE}
len_samp <- merge(sim$setdet, sim$samp, by = "set")
len_samp <- len_samp[len_samp$sim == 1 & len_samp$measured, ]
sim_icc <- round(icc(len_samp$length, len_samp$set), 1)
sim_icc <- sprintf("%.2f", sim_icc)
real_icc <- "0.70" # calculated in the file "imatate_cod_data.R"
```

>>>>

```{r packages, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
Sys.setenv("MAPBOX_TOKEN" = "pk.eyJ1IjoicGF1bHJlZ3VsYXIiLCJhIjoiY2pueGIxejMxMGM0MjNqbjR1aXdwYm92bSJ9.R-t1SCa0VHKf4N-PQmYI5Q")
source("analysis/paper/helper_functions.R")
```

@@

| `> abundance <- sim_abundance(`                         |                                       *Simulate abundance* |                            |         

@@

| `> grid <- make_grid(`                                  |                                              *Make a grid* |                            |

@@

| `> distribution <- sim_distribution(`                   |                                    *Simulate distribution* |                            |     
| `+   sim = abundance,`                                  |                Object produced by `sim_abundance` function |                            |     
| `+   grid = grid,`                                      |                    Object produced by `make_grid` function |                            |

@@

| `> surveys <- expand_surveys(`                          |                       *Define a series of surveys to test* |                            |

@@

| `> tests <- test_surveys(`                              |                             *Simulate and analyze surveys* |                            |
| `+   sim = distribution,`                               |             Object produced by `sim_distribution` function |                            |
| `+   surveys = surveys,`                                |               Object produced by `expand_surveys` function |                            |

@@

As noted above, the amount of RAM a user's computer has may limit the utility of the `sim_survey` function for running thousands of simulations of the same survey. The `sim_survey_parallel` function was therefore constructed to facilitate the running of thousands of simulations without running into RAM limitations. This function is set-up to run multiple `sim_survey` calls in parallel using the doParallel package [@weston2015] and, as such, multiple loops can be run using the `n_loops` argument and within each loop multiple simulations can be run (controlled using the `n_sims` argument). Total simulations will be the product of `n_loops` and `n_sims` arguments. If more than one core (`cores`) is specified, then the simulations will be run in parallel to speed up the process. Low numbers of `n_sims` and high numbers of `n_loops` will be easier on RAM, but may be slower. The optimum ratio of `n_sims` to `n_loops` will depend on the amount of RAM and number of cores the user's computer has. In any case, this function simplifies the process of running thousands of simulations of the same survey and the simulated data can then be supplied to survey-based or model-based analyses that require simulation testing.

@@

## Testing survey protocol

Assuming a stratified analysis as the default method for obtaining an index of abundance, a series of survey protocol can be tested using the `test_surveys` function. Provided a simulated population from `sim_distribution` and a series of survey protocol from `expand_surveys`, this function will simulate and analyze data from each survey using the `sim_survey`, `run_strat` and `strat_error` functions. Like `sim_survey_parallel`, this function operates in parallel and allows the specification of `n_sims` and `n_loops`, and the product of these two arguments equals the number of times each survey is simulated. Keep in mind that low numbers of `n_sims` and high numbers of `n_loops` will be easier on RAM, but may be slower, especially if the work is spread across few `cores`. The below code will run a small subset of the simulation tests run for the case study presented in this paper (see Table \@ref(tab:par) for code to replicate the case study results). Specifically, `expand_surveys` sets up a series of eight surveys to test (i.e. all possible combinations of `set_den`, `lengths_cap` and `ages_cap` protocol) and the `test_surveys` function will run 250 simulations of each survey and compare stratified estimates of abundance to the true abundance available to the survey. Though a limited test, this may take a while to run.

set.seed(438)
pop <- sim_abundance() %>%
  sim_distribution()

surveys <- expand_surveys(set_den = c(1, 2) / 1000,
                          lengths_cap = c(100, 500),
                          ages_cap = c(5, 20))

tests <- test_surveys(pop, surveys = surveys,
                      n_sims = 5, n_loops = 50, cores = 2)

Processing time will system (i.e. amount of RAM and number of cores) and setting (i.e. `n_loops` and `n_sims` ratio) dependent. The `test_survey` function will print a progress bar, generated using the progress package [@csardi2016], which details percent completion and will also include an eta after the first step of the loop completes. Thousands of simulations of hundreds of survey designs, like run here for our case study, may take days to run. The `test_surveys` function therefore includes an option for exporting intermediate results to a local directory, via the `export_dir` argument, and the `resume_test` function can be used resume a `test_surveys` run that had to be stopped part way through the process. The final object produced will be a list that includes all objects from `sim_abundance` and `sim_distribution` with the table of survey designs tested (named `surveys`) and tables produced by `strat_error` that end with the names `_strat_error` and `_strat_error_stats`. These tables include a `survey` column to allow merging of the survey protocol table with the error tables. Objects produced by `sim_survey` (set and sampling details) and `run_strat` (full stratified analysis results) are not retained to minimize object size. Like other core functions, some convenience functions are included in SimSurvey for creating interactive plots of the results from `test_surveys`. These will be demonstrated in the [Results] section using the results from the case study.

@@

Like any model, this simulation is a simplification of a much more complex reality. For instance, the population is assumed to aggregate by age-class and be uniformly distributed within a cell when, in the real-world, they may aggregate by length and form finer-scale clusters. The survey is also an instantaneous snapshot of the population, meaning that the population is assumed to be in the same location from the beginning to the end of the survey. Also, fish are aged at random within length bins and ages are estimated without error. Finally, area trawled is assumed to be perfectly standard. This is a short, non-inclusive, list of additional variability that likely occurs in the real-world but was not implemented here for simplicity. Nevertheless, the SimSurvey package provides the most realistic operating model that we are aware of for simulating stratified-random survey data from a population that varies across age, year and space dimensions.

@@

```{r data, cache = TRUE}
load("analysis/cod_sim_exports/2018-10-26_age_clust_test/test_output.RData")
tests <- sim
```
